%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=1.5cm, top=1.5cm, right=1.5cm, bottom=1.5cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts



% Color for highlights
\colorlet{awesome}{awesome-osu} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Ryan M.}{Scheirer}
\address{3928 NW Walnut Pl., Corvallis, OR 97330}
\mobile{(610) 597-7854}

\email{scheirer@oregonstate.edu}
\homepage{people.oregonstate.edu/\textasciitilde scheirer}
%\github{posquit0}
%\linkedin{posquit0}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}

%\position{Software Engineer{\enskip\cdotp\enskip}Security Expert} % Your expertise/fields
%\quote{``Make the change that you want to see in the world."} % A quote or statement

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------


\recipient{Company Recruitment Team}{Dog Inc.\\321 Stay St.\\Petoria, RI 27426} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Job Application for Middle Manager} % The title of the letter

\letteropening{Dear Mr./Ms./Dr. LastName,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

\letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

\makecvfooter{\today}{Ryan M. Scheirer~~~·~~~Cover Letter}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
  
%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header



\makelettertitle % Print the title

\vspace{0pt}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

\lettersection{About Me}

\hspace{10pt} My life has been driven by an innate desire to challenge myself to learn new things.  At the age of 16 I began what would become the most pivotal challenging endeavor in my life, learning to fly.  The stresses of being a high school student while taking flying lessons helped mold my adventurous nature.  While steadily making progress towards all my pilots’ certifications and ratings, I was introduced to the beautiful field of physics.  Unsatisfied by the basics principles that pilots are taught, I knew pursuing a degree in physics would satiate my need to challenge myself.  Sure enough, studying physics at the university level proved to be quite the challenge.  With my fancy new hard earned bachelor’s degree in physics, I decided to explore what opportunities it could pave for me.  I spent two years away from physics thinking I was done with academia, but physics wasn’t done with me.  The need to expand my knowledge while challenging myself lead me back to graduate school.  With the duties of being a TA and an RA, concurrent with all the coursework, physics graduate school offered a plethora of new challenges and obstacles.  Of all the seemingly insurmountable challenges that presented themselves to me, I grew found of the teaching duties.  Through teaching labs and recitations, I began to understand just how challenging teaching is.  Because teaching offers the unique opportunity to constantly test your own abilities while proving a supportive environment where students can test theirs, I decided to graduate with a master’s degree and begin what I believe now to be the most rewarding challenge in my life, teaching physics.

%------------------------------------------------

\lettersection{Why Teaching?}

\hspace{10pt} The needs and desires of college students are ever evolving as they are now coming from a new age of technology and ideology.  I believe teaching physics must also evolve to provide for the current student’s needs.  It is also imperative that the evolving teaching styles retain a rigorous study in content and goals.  The challenge of keeping up with the needs of current students while teaching physics is what will make me an effective teacher.  I have had the opportunity to practice new teaching styles for a few lectures of an algebra based physics course.  I also have been attending a new teaching seminar focused on physics education research for the past year.  And as a practicing teacher, I plan on continually seeking new ways to incorporate the latest physics education research in the classroom to help provide the current students with the best resources to succeed.

%------------------------------------------------

\lettersection{Why Me?}

  
\hspace{10pt} My personality drives me to work on challenging goals.  Teaching physics is not only just a challenge that I am excited to take on, but it is a discipline where I see the opportunity to challenge students to learn how physics will benefit their lives no matter where life takes them.


%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}